### 2018-08-22 doc/latex/03-Simulator.tex
Latest fixes
Add background information for gengeopop + template for other sections that have to be added to the manual

\item \texttt{-r} or \texttt{{-}-r0}: To obtain the basic reproduction number, no tertiary infections.

@@

\begin{description}
    \item[\texttt{--populationSize}] \ \\
        The size of the population to generate. By default a population of \texttt{6000000} is generated.
    \item[\texttt{--fracActive}] \ \\
        The fraction of people who are active, i.e. who are employed or students. By default \texttt{0.75} is used.
    \item[\texttt{--fracStudentCommuting}] \ \\
        The fraction of students commuting. By default \texttt{0.5} is used.
    \item[\texttt{--fracActiveCommuting}] \ \\
        The fraction of active people who commutes. By default \texttt{0.5} is used.
    \item[\texttt{--frac1826Students}] \ \\
        The fraction of 1826 years which are students. By default \texttt{0.5} is used.
    \item[\texttt{--household}] \ \\
        The file to read the household profiles from.
    \item[\texttt{--commuting}] \ \\
        The file to read the commuting information from.
    \item[\texttt{--cities}] \ \\
        The file to read the cities from.
    \item[\texttt{--subMinicipalities}] \ \\
        The file to read the sub-municipalities from.
    \item[\texttt{--output}] \ \\
        The file to write the GeoGrid to. By default this is \texttt{gengeopop.proto}
    \item[\texttt{--state}] \ \\
        The state to be used for initializing the random engine. This can be used to continue with the same state when generating multiple regions.
    \item[\texttt{--rng\_type}] \ \\
        The type of random engine to use by default \texttt{mrg2} is used. Available options are: \texttt{mrg2}, \texttt{mrg3}, \texttt{yarn2}, \texttt{yarn3}, \texttt{lgc64} and \texttt{lgc64\_shift}.
    \item[\texttt{--seed}] \ \\
        The seed to be used for the random engine. The default is \texttt{0}.
    \item[\texttt{--loglevel}] \ \\
        The loglevel to use, by default this is \texttt{info}.
\end{description}

>>>>

\item \texttt{-v} or \texttt{{-}-mapviewer}: Shows the MapViewer during simulation (only useful when using a GeoGrid).

@@

\begin{description}
    \item[\texttt{--populationSize}] \ \\
        The size of the population to generate. By default a population of \texttt{6000000} is generated.
    \item[\texttt{--fracActive}] \ \\
        The fraction of people who are active, i.e. who are employed or students. By default \texttt{0.75} is used.
    \item[\texttt{--fracStudentCommuting}] \ \\
        The fraction of students commuting. By default \texttt{0.5} is used.
    \item[\texttt{--fracActiveCommuting}] \ \\
        The fraction of active people who commutes. By default \texttt{0.5} is used.
    \item[\texttt{--frac1826Students}] \ \\
        The fraction of 1826 years which are students. By default \texttt{0.5} is used.
    \item[\texttt{--household}] \ \\
        The file to read the household profiles from.
    \item[\texttt{--commuting}] \ \\
        The file to read the commuting information from.
    \item[\texttt{--cities}] \ \\
        The file to read the cities from.
    \item[\texttt{--subMinicipalities}] \ \\
        The file to read the sub-municipalities from.
    \item[\texttt{--output}] \ \\
        The file to write the GeoGrid to. By default this is \texttt{gengeopop.proto}
    \item[\texttt{--state}] \ \\
        The state to be used for initializing the random engine. This can be used to continue with the same state when generating multiple regions.
    \item[\texttt{--seed}] \ \\
        The seed to be used for the random engine. The default is \texttt{0}.
    \item[\texttt{--loglevel}] \ \\
        The loglevel to use, by default this is \texttt{info}.
\end{description}
